%\documentclass{article}

\documentclass[12pt,letter,academicons]{article}
\usepackage[margin=1.75cm]{geometry}
\setlength{\columnsep}{1cm}

\usepackage{fontawesome}
\usepackage[hidelinks]{hyperref}
\usepackage{multicol}
\usepackage{tabularx}
\usepackage{tcolorbox}
\usepackage{varwidth}
\usepackage{xcolor}
\usepackage{academicons}
\usepackage{enumitem}


\definecolor{slateblue}{RGB}{61,75,105}
\definecolor{skyblue}{RGB}{210,225,241}
\definecolor{oceanblue}{RGB}{23,55,96}

\hypersetup{colorlinks=true, urlcolor=black}


\newcommand{\icon}[3]{% The first parameter is the FontAwesome icon name, the second is the box size and the third is the text
	\vcenteredhbox{\colorbox{skyblue}{\makebox(#2, #2){\textcolor{oceanblue}{\normalsize\csname fa#1\endcsname}}}}% Icon and box
	\hspace{0.35cm}% Whitespace
	\vcenteredhbox{\textcolor{black}{#3}}% Text
}

\newcommand*{\smallcaps}[1]{\textsc{#1}}
\newcommand*{\smallcapsalt}[1]{{\mdseries\smallcaps{#1}}}

\newcolumntype{L}{>{\raggedright\arraybackslash}X}
\newcolumntype{R}{>{\raggedleft\arraybackslash}X}
\newcolumntype{A}[1]{>{\hsize=#1\hsize\raggedright\arraybackslash}X}
\newcolumntype{D}[1]{>{\hsize=#1\hsize\raggedleft\arraybackslash}X}

\newsavebox{\myboxbox}
\NewDocumentEnvironment{mybox}{+b}% find a better name
 {%
  \centering
  \setlength{\parindent}{0pt}%
  % measure the text width
  \sbox{\myboxbox}{\begin{varwidth}{\columnwidth}#1\end{varwidth}}%
  \begin{tcolorbox}[
    breakable,
    width=\columnwidth,
    %top=0.2mm,
    %bottom=0.1mm,
    %left=0.1mm,
    %right=0.1mm,
    colback=skyblue,
    colframe=skyblue,
    sharp corners,
    %fontupper=\color{white},
    size=title
    ]
  #1
  \end{tcolorbox}%
 }{}



\begin{document}
\pagestyle{empty}
\begin{multicols}{2}
\begin{small}
\begin{center}
    \vspace*{2pt}\color{oceanblue}\Huge{\textbf{Ryne C. Johnston}}
\end{center}
\vspace*{-6pt}
\section*{\color{oceanblue}\smallcapsalt{Professional Experience}}
\hline

\begin{tabularx} {\columnwidth}{@{} L R @{}}
    \\[-6pt]Schr\"odinger, Inc. & Portland, OR\\
    \textbf{\textit{Product Manager}} & Jun 2023 -- Present
\end{tabularx}
\begin{itemize}
    \item Managed multiple products and directed teams to meet project goals and deadlines.
    \begin{itemize}
        \item \textit{Epik}: p\textit{K}\textsubscript{a} and protonation state predictor
        \item \textit{E-sol}: CNS permeability predictor
    \end{itemize}
    \item Interacted with customers and provided software solutions to meet their needs.
    \item Interacted with marketing and sales teams to develop and execute product launch plans.
\end{itemize}
\begin{tabularx} {\columnwidth}{@{} L R @{}}
    \\[-6pt]\textbf{\textit{Principal Scientist/}} & Jun 2021 -- Jun 2023\\
    \textbf{\textit{Technical Lead}}
\end{tabularx}
\begin{itemize}
    \item Developed and maintained best-in-class Python software to predict chemical properties through machine learning.
    \item Wrote scholarly articles and technical documents for public consumption.
    \item Wrote and maintained documentation and automated tests.
    \item Performed code reviews.
\end{itemize}
\begin{tabularx} {\columnwidth}{@{} L R @{}}
    \\[-6pt]\textbf{\textit{Senior Scientist}} & May 2017 -- Jun 2021\\
\end{tabularx}
\begin{itemize}
    \item Developed software to enumerate and canonicalize different related chemical compounds.
    \item Maintained legacy chemistry C/C++ software.
\end{itemize}
\begin{tabularx} {\columnwidth}{@{} L R @{}}
    \\[-6pt]Oak Ridge Nat'l Lab & Oak Ridge, TN\\
    \textbf{\textit{Postdoctoral Scholar}} & Jun 2015 -- Feb 2017\\
\end{tabularx}
\begin{itemize}
    \item Effectively communicated progress to a large, cross-disciplinary group of researchers.
    \item Wrote scholarly articles and research project proposals.
    \item Awarded nearly \$1M in research grant funds.
\end{itemize}

\columnbreak

\begin{mybox}
    \begin{itemize}
        \icon{Phone}{6} +1 (870) 403-2201\\
        \icon{Envelope}{6} {\href{mailto://rynecjohnston@gmail.com}{rynecjohnston@gmail.com}}\\
        \icon{Github}{6} {\href{https://github.com/rynecjohnston}{rynecjohnston}}\\
        \icon{MapMarker}{6} Beaverton, OR 97008
    \end{itemize}
\end{mybox}

\vspace*{-8pt}
\section*{\color{oceanblue}\smallcapsalt{Education}}
\hline
\begin{tabular} { r l }
    \\[-6pt]2015 & \textbf{Doctor of Philosophy}, Chemistry\\
    & \textit{Oregon State University} \\
    \\[-6pt]2010 & \textbf{Bachelor of Science}, Chemistry\\
    & \textit{Henderson State University}
\end{tabular}

\vspace*{-8pt}
\section*{\color{oceanblue}\smallcapsalt{Expertise}}
\hline
\vspace*{8pt}
p\textit{K}\textsubscript{a}, tautomerism, chemical equilibria, homogenous catalysis, cheminformatics

\vspace*{-8pt}
\section*{\color{oceanblue}\smallcapsalt{Skills}}
\hline
\vspace*{-6pt}
\begin{tabularx}{\columnwidth}{>{\hsize=.80\hsize\linewidth=\hsize}X
    >{\hsize=1.20\hsize\linewidth=\hsize}X}
    \begin{itemize}[itemsep=-2pt]
        \item Python
        \item PyData
        \item PyTorch
        \item RDKit
        \item git/GitHub
        \item C++
        \item Fortran
    \end{itemize} &
    \begin{itemize}[itemsep=-2pt]
        \item agile methodology
        \item productivity tools
        \item performance profilers
        \item computational\newline chemistry packages
        \begin{itemize}[itemsep=-2pt]
            \item Schr\"odinger
            \item ORCA
        \end{itemize}
    \end{itemize}
\end{tabularx}

\vspace*{-8pt}
\section*{\color{oceanblue}\smallcapsalt{Scientific Communication}}
\hline
\begin{tabularx} {\columnwidth}{@{} D{0.53} A{1.47} @{}}
    \\[-6pt]\multirow{}{}{\textit{Recent Conferences}} & Oral presentation at the American Chemical Society National Meeting, Spring 2021\\
    \\\multirow{}{}{\textit{\href{https://scholar.google.com/citations?user=wAcCco0AAAAJ}{Selected Publications (from \textgreater25)}}} & Johnston, R. C. et al. Epik: p\textit{K}\textsubscript{a} and Protonation State Prediction through Machine Learning \textit{Journal of Chemical Theory and Computation}, \textbf{2023}, \textit{19}, 2380-2388, doi: {\href{https://dx.doi.org/10.1021/acs.jctc.3c00044}{10.1021/acs.jctc.3c00044}}.
\end{tabularx}

\vspace*{-12pt}
\section*{\color{oceanblue}\smallcapsalt{Interests}}
\hline
\vspace*{12pt}
chemistry, geology, history, programming, hiking

\end{small}
\end{multicols}
\end{document}
